Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-25 WSSSPE1_report/WSSSPE1_summary_report.tex
proof read pass over abstract

\begin{abstract} %\note{Lead: Sou-Cheng T. Choi}
% Anne: Added a lead-in motivator to address the submission as a Experience paper
% and tried to improve writing... ( I am assumeing no abstract word count limit...)
Challenges related to the development, deployment, and maintenance of 
reusable software for science is becoming an increasing concern. 
There are now many scientists whose research increasingly depends on 
the quality and availability of software they can use and build on. 
At the same time, software specialists have more than enough to do 
without having to "reinvent the wheel". To highlight some of these 
issues and share experiences, The First Workshop on Sustainable 
Software for Science: Practice and Experiences (WSSSPE1) was held 
in November 2013 at SC13.
The workshop featured keynote presentations and based its discussion 
them, as well as on a large number (54) of solicited extended abstracts 
that were grouped into three themes presented via panels that encouraged 
audience participation. A set of collaborative notes was taken during the workshop.

This document 
% article? 
summarizes 
the issues and shared experiences discussed atthe workshop, including
cross-cutting issues and use cases. It joins a nascent
literature seeking to understand what drives software work in science,
and how it is impacted by the reward systems of science. 
These incentives can determine the extent to which
developers are motivated to build software for the long-term, for the
use of others, and whether to work collaboratively or separately.

>>>>

\begin{abstract} %\note{Lead: Sou-Cheng T. Choi}
% Anne: Added a lead-in motivator to address the submission as a Experience paper
% and tried to improve writing... ( I am assumeing no abstract word count limit...)
Challenges related to the development, deployment, and maintenance of reusable
software for science is becoming an increasing concern.  There are now many
scientists whose research increasingly depends on the quality and availability
of software they can use and build on.  At the same time, software specialists
have more than enough to do without having to "reinvent the wheel". To
highlight some of these issues and share experiences, The First Workshop on
Sustainable Software for Science: Practice and Experiences (WSSSPE1) was held
in November 2013 at SC13.  The workshop featured keynote presentations and
based its discussion on them, as well as on a large number (54) of solicited
extended abstracts that were grouped into three themes presented via panels
that encouraged audience participation. A set of collaborative notes was taken
during the workshop.

This document % article? 
summarizes the issues and shared experiences discussed at the workshop,
including cross-cutting issues and use cases. It joins a nascent literature
seeking to understand what drives software work in science, and how it is
impacted by the reward systems of science.  These incentives can determine the
extent to which developers are motivated to build software for the long-term,
for the use of others, and whether to work collaboratively or separately.
